\chapter{Methodology}
{\color{red} 
	
	The initial step of this master thesis work was to quantify the characteristics of two hypothetical types of constraints in industrial production: technology-driven constraints and load-driven constraints. 
	
	I am planning to achieve this with an Operations Research Model consists of two steps. First, analyzing the statistical properties of association networks over Time in an extensive data set from steel manufacturing; second, developing an abstract theoretical framework to understand better the connection between each type of constraint and the statistical patterns created by them. 
	
}

{\color{red} 
	
	Introduce proposed concepts in the Operations Research Model (OR model).
	
	The OR model is a combination of Steel Manufacturing Events Analysis and Flux Balance Analysis. The art form of this model is to structure a standard data format and a shared analysis logic that allows comparing the results from manufacturing data and simulation data.
	
	A brief introduction for Association Networks and FBA. 
	An explanation for generating a data structure with OR-modeling in the combination of those. More detailed information to be given in the Backgroud Information Section, guiding the readers who have knowledge of FBA and Association Network concepts to the Concept Implementation Section.
	
	Usage of linear programming and generating sets of synthetic data allow comparing the statistical characteristics of their association network with those created from the real-world data set from steel manufacturing.
	
}

\input{steel-manufacturing-data-analysis}
\input{flux-balance-analysis}
